\documentclass[11pt, a4paper, roman]{letter}

\usepackage[top = 12mm, bottom = 12mm, left=10mm, right=10mm]{geometry} %determines page margins / document formatting
\usepackage[T1]{fontenc}  % We are using pdfLaTeX,
\usepackage[utf8]{inputenc} %allows direct input of accented characters
\usepackage{ragged2e} %allows for right aligned / left aligned text instead of all justified

\usepackage[UKenglish]{babel} %sets hypenation / spelling etc
\usepackage[stretch = 25, shrink = 25]{microtype}  %for better formatting of words in a line / sentence


\usepackage{graphicx} %Required for inserting images
\usepackage{fontawesome} %for nice icons

\usepackage{fancyhdr} %to create header and footer

\usepackage{enumitem} % To redefine spacing in lists

\usepackage{xcolor} %To add colour to the document
\definecolor{cvteal}{HTML}{008080} %Change this to be any hexcode
\definecolor{cvblue}{HTML}{304263} %Change this to be any hexcode
\usepackage[colorlinks = true, urlcolor = black, linkcolor = white]{hyperref}

\begin{document}

%-------------------------------------------------------------------------------
% Fonts
%-------------------------------------------------------------------------------

% How to define a font using a .ttc file (where all the fonts are in a single file):
% \newfontfamily{\Noteworthy}{Noteworthy.ttc}[
%     Ligatures = TeX ,
%     Path = /System/Library/Fonts/ ,
%     UprightFeatures = {FontIndex=0} ,
%     BoldFeatures = {FontIndex=1} ,
%     ItalicFeatures = {FontIndex=2} ,
%     BoldItalicFeatures = {FontIndex=3} ,
% ]

\newfontfamily{\TimesNewRoman}{Times New Roman}

% How to define a font using a .ttf file:
% Define a new font to be used for headers
\newfontfamily{\Garamond}{CormorantGaramond}[
    Ligatures = TeX ,
    Scale = 1.0,
    Path = /Library/Fonts/ ,
    Extension = .ttf ,
    UprightFont = *-regular ,
    BoldFont = *-bold ,
    ItalicFont = *-italic ,
    BoldItalicFont = *-bolditalic
]

% How to define the light version of a font in a .ttf file:
% % Define a new font to be used for headers
% \newfontfamily{\GaramondLight}{CormorantGaramond}[
%     Ligatures = TeX ,
%     Path = /Library/Fontsbtop/ ,
%     Extension = .ttf ,
%     UprightFont = *-Light ,
%     ItalicFont = *-LightItalic ,
% ]

% Define the light version of the helvetica font in the .ttc file
\newfontfamily\HelveticaLight{Helvetica.ttc}[
    Ligatures = TeX ,
    Path = /System/Library/Fonts/ ,
    UprightFeatures = {FontIndex=4} ,
]

% This command gives the ability to format text as the light font face, e.g. `\lightfont{Hello World}`
\newcommand\lightfont[1]{{\HelveticaLight#1}}

% Set the main font
\setmainfont{Helvetica}

\pagestyle{empty}
\raggedbottom

\begin{minipage}[t]{0.5\textwidth}
    \vspace*{\fill}
    \textsc{{\TimesNewRoman \Huge Hunter Ducharme}}
    \vspace*{\fill}
\end{minipage}\hfill
\begin{minipage}[t]{0.3\textwidth}
    \setlength{\baselineskip}{15pt}
    \RaggedLeft 
    \faMobile{} 281-450-7154\\
    \faHome{} Santa Barbara, CA\\ 
    \faEnvelope {} hgducharme@gmail.com\\ 
    \faLinkedinSquare{} /in/hunterducharme\\
    \faGithub{} /hgducharme
\end{minipage}

{\color{cvteal} \rule{\linewidth}{1mm}}

\begin{minipage}[t]{\textwidth}
\begin{letter}{}
    
\setlength{\parskip}{5pt} %set inter-parapgraph distance
\setlength{\baselineskip}{15pt} %set inter-line distance
    \opening{Dear Hiring Manager,}

    \begin{center} {\textbf{Position:} \underline{Job Title / Name (Vacancy ID)}} \end{center}

\setlength{\parskip}{20pt}

\justifying{

I am writing to express my interest in this role. After putting a temporary hold on my corporate career, I decided to pursue adventurous roles, including firefighting, while I am physically capable. These experiences have allowed me to broaden my horizons and build resilience, but I have also remained actively engaged in software development and problem-solving during this time.

I have worked on several math and software projects, including developing a C++ chess engine from scratch and founding HighlightTools, a startup in its early stages. Additionally, I have completed freelance projects for two clients. One project, AstroCarto, involved designing astronomy algorithms, while another required me to create a Python script that analyzed and simulated trading data from Excel files for a private client.

I am excited to return to a more traditional tech role and would love the opportunity to contribute my unique experiences and technical skills to your team. I am confident that my background in both adventurous and technical pursuits has prepared me to tackle new challenges with creativity and determination.

Thank you for considering my application. I look forward to the possibility of discussing how I can contribute to your team.

}   
\end{letter}
\end{minipage}

\vspace*{\fill}
Best regards,\\\textbf{Your Name}
\vspace*{\fill}

\end{document}
