%-------------------------------------------------------------------------------
% Experience
%-------------------------------------------------------------------------------

\newcommand{\Sundowners}{
\noindent
\textbf{U.S. Forest Service, Crew 8 (Sundowners)} \hfill Ojai, CA\\
\textit{Forestry Technician - Wildland Firefighter} \hfill May 2024 - Present
\begin{itemize}
    \item Member of a 16-person Type II hand crew, adeptly navigating dynamic, high-stress, and hazardous environments
    \item Proficiently operated in steep and uneven terrain on extended shifts while carrying gear exceeding 45 lbs.
    \item Crew responsibilities included fire line construction, fuels suppression and reduction, and mop-up tasks
    \item Utilized hand tools to construct fire lines, ensuring effective containment and control.
    \item Demonstrated leadership as the lead EMT, overseeing crew medical concerns and emergencies
    \item Diligently conducted daily vehicle inspections and station upkeep, ensuring operational readiness
    \item Maintained vigilant situational awareness, monitoring for potential hazards and changing conditions
    \item Communicated effectively with team members to achieve project goals while prioritizing team safety
\end{itemize}
}

\newcommand{\AstroCarto}{
\noindent
\textbf{AstroCarto} \hfill Santa Barbara, CA\\
\textit{Contracted Software Developer} \hfill December 2024 - March 2024
\begin{itemize}
    \item Designed and implemented a flask API that performs precise astronomy calculations given a moment in time
    \item Utilized JPL's DE441 ephemeris to accurately compute planetary state vectors
    \item Applied spherical geometry to calculate the boundary of the Earth's visible portion for a distant observer
    \item Utilized Lunar osculating orbital elements to calculate the position of the lunar ascending node
    \item Used the Skyfield library for advanced timekeeping, JPL ephemeris parsing, and planetary subpoint determination
    \item Successfully negotiated contract terms with clients, defining clear deliverables and specs to ensure project alignment
\end{itemize}
}

\newcommand{\OdysseySpaceResearch}{
\noindent
\textbf{Odyssey Space Research} \hfill Houston, TX\\
\textit{Aerospace Engineer and Software Developer} \hfill February 2020 - August 2022
\begin{itemize}
    \item Verified GNC/trajectory designs of ISS-visiting vehicles for rendezvous, proximity, and capture (RPOC) operations.
    \item Determined solar array blockage based on vehicle position data using basic computational geometry and Python.
    \item Worked on the National Team's Lunar Lander doing modeling and simulation development in C++.
    \item Developed a planetary magnetic field model in C++ for an orbit determination/propagation simulation.
    \item Developed code for a Node.js web application designed to display Orion spacecraft telemetry data.
    \item Performed hardware and software integration for Orion and Lunar Lander Trick-based simulations.
\end{itemize}
}

\newcommand{\NassauBayFD}{
\noindent
\textbf{Nassau Bay Fire Department} \hfill Nassau Bay, TX\\
\textit{Volunteer Firefighter/EMT} \hfill May 2020 - February 2022
\begin{itemize}
    \item Volunteered as a firefighter/EMT and provided protection of life and property to the Nassau Bay community
    \item Responded to 911 emergency service calls including fire, motor vehicle accidents, EMS calls, and rescue situations
    \item Provided initial medical care including patient assessment and stabilization until mutual aid EMS arrived on scene
    \item Actively participated in inspecting and maintaining all equipment around the station and on the fire apparatuses
    \item Completed weekly trainings such as confined space drills and practice in initial attacks and vertical ventilation
\end{itemize}
}

\newcommand{\SentriForce}{
\noindent
\textbf{SentriForce} \hfill Houston, TX\\
\textit{Contracted Full Stack Web Developer} \hfill June 2019 - August 2022
\begin{itemize}
    \item Designed and built a custom web application to toggle computers on remote networks.
    \item Cut original task completion time by approximately 90\%.
    \item Performed full-stack web development using Python/Django, HTML, CSS, andJavaScript.
    \item Integrated a third-party REST API to fetch data from an online database.
    \item Deployed web-application on an Ubuntu server using Nginx and Gunicorn.
\end{itemize}
}

\newcommand{\MilkAndHoney}{
\noindent
\textbf{Milk \& Honey} \hfill Santa Barbara, CA\\
\textit{Bartender/Closing Shift Lead} \hfill June 2023 – March 2024
\begin{itemize}
    \item Maintained a key to the restaurant for closing and opening purposes.
    \item Demonstrated proficiency in multitasking, time-management, and maintaining exceptional cleanliness of the bar.
    \item Provided full service (food and drink) at the bar top while providing exceptional customer service to bar patrons.
    \item Actively contributed to the development and refinement of the cocktail menu.
    \item Demonstrated strong attention to detail with consistent use of a jigger and artistically garnishing each cocktail.
    \item Develop and maintain relationships with regular customers, creating a welcoming and friendly atmosphere.
    \item Upheld strict adherence to all relevant health and liquor regulations, ensuring a safe and enjoyable environment.
\end{itemize}
}

\newcommand{\Eureka}{
\noindent
\textbf{Eureka!} \hfill Santa Barbara, CA\\
\textit{Bartender} \hfill January 2023 – June 2023
\begin{itemize}
    \item Selected as one of the primary night-time bartenders.
    \item Proven ability to handle 15 seats at the bar while making drinks for the whole restaurant.
    \item Consistently used jigger to create balanced cocktails while providing exceptional customer service to patrons.
    \item Develop and maintain relationships with regular customers, creating a welcoming and friendly atmosphere.
    \item Collaborate with other team members to ensure seamless service and a positive experience for all guests.
    \item Manage inventory, ensuring that all supplies are well-stocked and prepared for busy shifts.
\end{itemize}
}

\newcommand{\DoorDash}{
\noindent
\textbf{DoorDash} \hfill Houston, TX and Santa Barbara, CA\\
\textit{Delivery Driver} \hfill March 2020 – January 2023
\begin{itemize}
    \item Communicate with customers to ensure deliveries are completed accurately and on-time.
    \item Interact professionally with restaurant staff to obtain the correct order with the customer’s desired items.
    \item Fulfill dispatched orders in a timely manner while practicing defensive driving.
    \item Maintained a 4+ star customer rating by communicating effectively and ensuring food is hot upon delivery.
\end{itemize}
}

\newcommand{\Marvinos}{
\noindent
\textbf{Marvino’s Italian Kitchen} \hfill Houston, TX\\
\textit{Barback} \hfill April 2019 – March 2020
\begin{itemize}
    \item Greeted customers with silverware, bread, olive oil, and initial non alcoholic beverage orders.
    \item Maintained cleanliness of the bar by bussing all customer seats at the bar and wiping down bar top.
    \item Washed the entire bar down during closing shifts including floor mats.
\end{itemize}
}

\newcommand{\LakeridgeTownhomes}{
\textbf{Lakeridge Townhomes} \hfill College Station, TX\\
\textit{Maintenance} \hfill August 2016 – December 2019
\begin{itemize}
    \item Promoted horizontally from construction laborer to head of maintenance.
    \item In charge of repairing and fixing maintenance requests for 150 apartment units.
    \item Maintained cleanliness of the apartment grounds ensuring no visible trash.
\end{itemize}
\textit{Construction Laborer} \hfill June 2016 – August 2016
\begin{itemize}
    \item Performed general labor for 10 intense weeks during construction of four new, 3-story apartment buildings.
    \item Cleaned construction site including sweeping dirt, removing drywall and broken brick, moving doors, and picking up trash.
    \item Utilized basic hand tools and heavy machinery, including skill saws, Bobcat loaders, and Genie forklifts.
    \item Provided general maintenance for Lakeridge residents.
\end{itemize}
}

\newcommand{\LakeridgeTownhomesMaintenance}{
\textbf{Lakeridge Townhomes} \hfill College Station, TX\\
\textit{Maintenance} \hfill August 2016 – December 2019
\begin{itemize}
    \item Promoted horizontally from construction laborer to head of maintenance.
    \item In charge of repairing and fixing maintenance requests for 150 apartment units.
    \item Maintained cleanliness of the apartment grounds ensuring no visible trash.
\end{itemize}
}

\newcommand{\LakeridgeTownhomesLaborer}{
\textbf{Lakeridge Townhomes} \hfill College Station, TX\\
\textit{Construction Laborer} \hfill June 2016 – August 2016
\begin{itemize}
    \item Performed general labor for 10 intense weeks during construction of four new, 3-story apartment buildings.
    \item Cleaned construction site including sweeping dirt, removing drywall and broken brick, moving doors, and picking up trash.
    \item Utilized basic hand tools and heavy machinery, including skill saws, Bobcat loaders, and Genie forklifts.
    \item Provided general maintenance for Lakeridge residents.
\end{itemize}
}

\newcommand{\Engineering}{\AstroCarto \OdysseySpaceResearch \SentriForce}
\newcommand{\FireEMS}{\Sundowners \NassauBayFD \LakeridgeTownhomes}
\newcommand{\ServiceIndustry}{\MilkAndHoney \Eureka \DoorDash \Marvinos}