% Document class and font size
\documentclass[a4paper,9pt]{extarticle}

% Packages
\usepackage[utf8]{inputenc} % For input encoding
\usepackage{geometry} % For page margins
\geometry{a4paper, margin=0.75in} % Set paper size and margins
\usepackage{titlesec} % For section title formatting
\usepackage{enumitem} % For itemized list formatting
\usepackage{hyperref} % For hyperlinks

%-------------------------------------------------------------------------------
% Formatting
%-------------------------------------------------------------------------------
% Removes item separation
\setlist{noitemsep}

% Section title format
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule]

% Section title spacing
\titlespacing*{\section}{2pt}{\baselineskip}{\baselineskip}

% Disable page numbers
\pagestyle{empty}

\newcommand\tab[1][1cm]{\hspace*{#1}}

%-------------------------------------------------------------------------------
% Begin Document
%-------------------------------------------------------------------------------

\begin{document}

%-------------------------------------------------------------------------------
% HEADER
%-------------------------------------------------------------------------------
\begin{center}
\textbf{\Large Hunter Ducharme}\\[2pt]
hgducharme@gmail.com | (281) 450-7154 | Santa Barbara, CA
\end{center}

%-------------------------------------------------------------------------------
% Summary
%-------------------------------------------------------------------------------
\newcommand{\BartendingSummary}{I’m an experienced bartender with a passion for creating exceptional cocktails and providing excellent customer service. I have a proven track record of working efficiently in high-pressure environments while maintaining a friendly atmosphere and work environment. I am dedicated, reliable, and a team player looking to work with like-minded individuals who are committed to the success of the establishment.}

\newcommand{\FireSummary}{I’m an extremely dedicated and physically fit individual looking to extend my passion for the outdoors and serving the public through a wildland firefighting position. I have a proven track record working in a team environment in high stress situations, and am eager to contribute my efforts towards wildfire prevention, containment, and restoration efforts.}

% \section*{SUMMARY}
% \FireSummary

%-------------------------------------------------------------------------------
% Education
%-------------------------------------------------------------------------------
\section*{EDUCATION}

\noindent
\textbf{Texas A\&M University}, College Station, TX \hfill December 2019\\
B.Sc. Double Major \hfill GPA: 3.12/4.0\\
Mathematics and Aerospace Engineering

%-------------------------------------------------------------------------------
% Experience Macros
%-------------------------------------------------------------------------------

\newcommand{\AstroCarto}{
\noindent
\textbf{AstroCarto} \hfill Houston, TX\\
\textit{Contracted Aerospace Engineer} \hfill December 2024 - March 2024
\begin{itemize}
    \item Developed a software application that calculates astronomy related algorithms.
    \item Calculated the boundary of the visible portion of the Earth for a fictituous observer anywhere away from the Earth.
    \item Calculated the subpoint great circle for any celestial interest.
    \item Utilizied Python astronomy library Skyfield and JPL ephemerides.
\end{itemize}
}

\newcommand{\OdysseySpaceResearch}{
\noindent
\textbf{Odyssey Space Research} \hfill Houston, TX\\
\textit{Aerospace Engineeer and Software Developer} \hfill Febuary 2020 - August 2022
\begin{itemize}
    \item Verified GNC/trajectory designs of ISS-visiting vehicles for rendezvous, proximity, and capture (RPOC) operations.
    \item Determined solar array blockage based on vehicle position data using basic computational geometry and Python.
    \item Worked on the National Team's Lunar Lander doing modeling and simulation development in C++.
    \item Developed a planetary magnetic field model in C++ for an orbit determination/propagation simulation.
    \item Developed code for a Node.js web application designed to display Orion spacecraft telemetry data.
    \item Performed hardware and software integration for Orion and Lunar Lander Trick-based simulations.
\end{itemize}
}

\newcommand{\SentriForce}{
\noindent
\textbf{SentriForce} \hfill Houston, TX\\
\textit{Contracted Full Stack Web Developer} \hfill June 2019 - August 2022
\begin{itemize}
    \item Designed and built a custom web application to toggle computers on remote networks.
    \item Cut original task completion time by approximately 90\%.
    \item Performed full-stack web development using Python/Django, HTML, CSS, andJavaScript.
    \item Integrated a third-party REST API to fetch data from an online database.
    \item Deployed web-application on an Ubuntu server using Nginx and Gunicorn.
\end{itemize}
}

\newcommand{\MilkAndHoney}{
\noindent
\textbf{Milk \& Honey} \hfill Santa Barbara, CA\\
\textit{Bartender/Closing Shift Lead} \hfill June 2023 – March 2024
\begin{itemize}
    \item Maintained a key to the restaurant for closing and opening purposes.
    \item Demonstrated proficiency in multitasking, time-management, and maintaining exceptional cleanliness of the bar.
    \item Provided full service (food and drink) at the bar top while providing exceptional customer service to bar patrons.
    \item Actively contributed to the development and refinement of the cocktail menu.
    \item Demonstrated strong attention to detail with consistent use of a jigger and artistically garnishing each cocktail.
    \item Develop and maintain relationships with regular customers, creating a welcoming and friendly atmosphere.
    \item Upheld strict adherence to all relevant health and liquor regulations, ensuring a safe and enjoyable environment.
\end{itemize}
}

\newcommand{\Eureka}{
\noindent
\textbf{Eureka!} \hfill Santa Barbara, CA\\
\textit{Bartender} \hfill January 2023 – June 2023
\begin{itemize}
    \item Selected as one of the primary night-time bartenders.
    \item Proven ability to handle 15 seats at the bar while making drinks for the whole restaurant.
    \item Consistently use jigger to create hand-crafted cocktails while providing exceptional customer service to bar patrons.
    \item Develop and maintain relationships with regular customers, creating a welcoming and friendly atmosphere.
    \item Collaborate with other team members to ensure seamless service and a positive experience for all guests.
    \item Manage inventory, ensuring that all supplies are well-stocked and prepared for busy shifts.
\end{itemize}
}

\newcommand{\DoorDash}{
\noindent
\textbf{DoorDash} \hfill Houston, TX and Santa Barbara, CA\\
\textit{Delivery Driver} \hfill August 2020 – January 2023
\begin{itemize}
    \item Communicate with customers to ensure deliveries are completed accurately and on-time.
    \item Interact professionally with restaurant staff to obtain the correct order with the customer’s desired items.
    \item Fulfill dispatched orders in a timely manner while practicing defensive driving.
    \item Maintained a 4+ star customer rating by communicating effectively and ensuring food is hot upon delivery.
\end{itemize}
}

\newcommand{\Marvinos}{
\noindent
\textbf{Marvino’s Italian Kitchen} \hfill Houston, TX\\
\textit{Barback} \hfill April 2019 – March 2020
\begin{itemize}
    \item Greeted customers with silverware, bread, olive oil, and initial non alcoholic beverage orders.
    \item Maintained cleanliness of the bar by bussing all customer seats at the bar and wiping down bar top.
    \item Washed the entire bar down during closing shifts including floor mats.
\end{itemize}
}

\newcommand{\LakeridgeTownhomes}{
\textbf{Lakeridge Townhomes} \hfill College Station, TX\\
\textit{Maintenance} \hfill June 2016 – December 2019
\begin{itemize}
    \item Promoted horizontally from construction laborer to head of maintenance.
    \item In charge of repairing and fixing maintenance requests for 150 apartment units.
    \item Maintained cleanliness of the apartment grounds ensuring no visible trash.
\end{itemize}
\textit{Construction Laborer} \hfill June 2016 – December 2019
\begin{itemize}
    \item Performed general labor for 10 intense weeks during construction of four new, 3-story apartment buildings.
    \item Cleaned construction site including sweeping dirt, removing drywall and broken brick, moving doors, and picking up trash.
    \item Utilized basic hand tools and heavy machinery, including skill saws, Bobcat loaders, and Genie forklifts.
    \item Provided general maintenance for Lakeridge residents.
\end{itemize}
}

\newcommand{\NassauBayFD}{
\noindent
\textbf{Nassau Bay Fire Department} \hfill Nassau Bay, TX\\
\textit{Volunteer Firefighter/EMT} \hfill May 2020 - Febuary 2022
\begin{itemize}
    \item Volunteered as a firefighter/EMT and provided protection of life and property to the Nassau Bay community
    \item Responded to 911 emergency service calls including fire, motor vehicle accidents, EMS calls, and rescue situations
    \item Provided initial medical care including patient assessment and stabilization until mutual aid EMS arrived on scene
    \item Actively participated in inspecting and maintaining all equipment around the station and on the fire apparatuses
    \item Completed weekly trainings such as confined space drills and practice in initial attacks and vertical ventilation
\end{itemize}
}

\newcommand{\Engineering}{\AstroCarto \OdysseySpaceResearch \SentriForce}
\newcommand{\FireEMS}{\NassauBayFD \LakeridgeTownhomes}
\newcommand{\ServiceIndustry}{\MilkAndHoney \Eureka \DoorDash \Marvinos}

%-------------------------------------------------------------------------------
% Experience Section
%-------------------------------------------------------------------------------
\section*{RELEVANT EXPERIENCE}

\Engineering

%-------------------------------------------------------------------------------
% Project Macros
%-------------------------------------------------------------------------------
\newcommand{\Meatball}{
\noindent
\textbf{Meatball - Chess Engine (work in progress)} \hfill March 2022 - Present\\
\textit{Project Link:} \url{https://github.com/hgducharme/meatball}
\begin{itemize}
    \item Building a chess engine in C++17 entirely from scratch.
    \item Implemented efficient move generation using bitboards, magic bitboards, and a perft function.
    \item Develop the code base with intense focus on readability, maintainability, and adherence to SOLID principles
    \item Designed and implemented a full build process, test suite, and coverage report generation.
    \item Built a Lichess bot in Python to interface between the chess engine and the Lichess.com API.
    \item Demonstrated an excellent ability to understand complex topics and translate them into code.
\end{itemize}
}

\newcommand{\InvertedPendulum}{
\noindent
\textbf{Inverted Pendulum Control System} \hfill July 2019 - September 2019\\
\textit{Project Link:} \url{https://github.com/hgducharme/inverted-pendulum}
\begin{itemize}
    \item Built an entirely custom inverted pendulum embedded system.
    \item Derived the second-order nonlinear dynamic model using Lagrangian dynamics.
    \item Converted the dynamic model to a linearized state-space model.
    \item Built a simulation/validation environment in Python to help design the LQR controller.
    \item Performed embedded software by implementing LQR control on a microcontroller using C++.
\end{itemize}
}

%-------------------------------------------------------------------------------
% Project Section
%-------------------------------------------------------------------------------
\section*{PROJECTS}

\Meatball
\InvertedPendulum

%-------------------------------------------------------------------------------
% Skills, Coursework, Certification Macros
%-------------------------------------------------------------------------------

\newcommand{\EngineeringSkills}{
\section*{SKILLS \& COURSEWORK}
\begin{itemize}
    \item \textbf{Programming Languages:} Python, C++, Node.js, HTML, CSS, JavaScript, Bash
    \item \textbf{Math Coursework:} Real analysis, abstract algebra, differential geometry, complex analysis, partial differential equations, linear algebra I \& II, numerical methods, discrete mathematics, probability
    \item \textbf{Engineering Coursework:} Spacecraft attitude dynamics and control (graduate level), vehicle stability and control, active controls, numerical methods, astrodynamics, computational aerospace structural design (graduate level)
\end{itemize}
}

\newcommand{\FFCertifications}{
\section*{Certifications}
\begin{itemize}
    \item NFPA 1001: Structural Firefighter 1 and 2 — IFSAC Certified
    \item NFPA 1072: HAZMAT Awareness and Operations — IFSAC Certified
    \item EMT-Basic — California EMT and NREMT
\end{itemize}
}

%-------------------------------------------------------------------------------
% Skills, Coursework, Certification Section
%-------------------------------------------------------------------------------

\EngineeringSkills

\end{document}